\documentclass[addpoints, 12pt]{exam}
\pagestyle{headandfoot}
\firstpageheader{Name:}{Precalculus Final Exam}{February 20, 2013}
\firstpageheadrule
\pointsinmargin
\usepackage{amsmath}
\noprintanswers

\begin{document}
\begin{questions}


\question Consider the function $f(x) = \sqrt{-3x + 2}$

\begin{parts}
\part What are the possible outputs of this function?
\part Give another function that has the same set of possible inputs, but a different set of possible outputs.
\part Give another function that has the same set of possible outputs, but a different set of possible inputs.
\end{parts}

\question Consider the functions $f(x) = \sqrt{x+5}$ and $g(x) = x^2 + 3$
\begin{parts}
\part State the domain and range of each function
\part Find the composition $f(g(x))$.  What is its domain and range?
\part Find the composition $g(f(x))$.  What is its domain and range?
\part (BONUS) Find a function $h(x)$ such that $h(g(x)) = 1$
\end{parts}

\question The following are lengths of sides of right triangles, in order of increasing size.  Find the length of the missing side:
\begin{parts}
\part 3, x, 6
\part  4, 4, x
\end{parts}


\question Draw a unit circle, labelling angles ($0, \frac{\pi}{6}, \frac{\pi}{4}, \frac{\pi}{3}, \ldots$) and showing the \emph{definitions} (but not the values) of the sine, cosine, secant, cosecant, and tangent functions.

\question A wheel of radius 30 centimeters turns through 4.5 revolutions in 45 seconds.
\begin{parts}
\part By what angle (in radians) does the wheel turn?
\part How far does the vehicle attached to the wheel travel?
\part Consider a point on the wheel that is initially in contact with the ground.  Construct a function that describes the height of that point above the ground as the wheel turns.
\part Graph the function in (c) for times between 0 and 45 seconds.
\end{parts}

\question Bacteria grow in a process in which each bacteria cell splits in half every 20 minutes.  Imagine that you are infected by a single bacteria at Noon.
\begin{parts}
\part What time will it be when there are 6 million (or more) bacteria present?
\part Suppose you have a detergent that can kill exactly two-thirds of any bacteria present each time you wash with it.  Obviously, you will have to apply it more than once to get the number of bacteria back below 1.  How many times will you have to use the detergent?
\part Make sure to express the processes in a and b using expressions that involve exponents.
\end{parts}

\question (BONUS) Determine at what time of day the image of the Washington Monument must have been taken.  The monument itself is 552 feet tall.  Make sure to explain your reasoning clearly.

\end{questions}

\end{document}

